---
title: "Lab 9"
author: "Bora Joo"
format: 
  html:
    self-contained: true
    code-tools: true
    code-fold: true
editor: visual
execute:
  echo: true
  error: true
---

```{r}
#| message: false
library(tidyverse)
library(gt)
```

```{r}
#| message: false
names_a <- read_csv(here::here("labs", "lab9", "StateNames_A.csv"))
names_a |>
  head() |>
  DT::datatable()
```

## **3. Summarizing & Visualizing the Number of Allisons**

```{r q1}
#| message: false
allisons <- names_a |>
  rename(Sex = Gender) |>
  filter(Name == "Allison") |>
  group_by(State, Sex) |>
  summarize("Count of sex" = sum(Count), .groups = "drop") |>
  pivot_wider(names_from = "Sex", values_from = "Count of sex", values_fill = 0)
allisons |>
  DT::datatable()
```

```{r q2}
allison_f <- names_a |>
  rename(Sex = Gender) |>
  filter(Name == "Allison", Sex == "F")
```

```{r}
allison_f |>
  group_by(Year) |>
  summarize(Count = sum(Count)) |>
  ggplot(mapping = aes(x = Year, y = Count)) +
  geom_line() +
  labs(y = NULL, title = "Number of babies named Allison over the years")

```

## **4. Modeling the Number of Allisons**

```{r q4}
allison_lm <- lm(formula = Count ~ Year, data = allison_f)
allison_lm |>
  group_by()
  broom::augment() |>
  DT::datatable()
```

5.  number of babies named Allison in a year = 3894.356 - 1.882 \* year

```{r q6}
allison_lm |>
  broom::augment() |>
  ggplot(mapping = aes(y = .resid, x = .fitted)) +
  geom_point()
```

7.  Most of the points on the residual plot are clustered near the bottom of the graph, rather than being evenly distributed around the plot. Based on this, a linear regression model does not predict the number of babies named "Allison" by year. It is indeterminate whether year can correctly predict the number of "Allison"s or not.

## **5. Spelling by State**

```{r q8}
#| message: false
names_a |>
  filter(Name %in% c("Alan", "Allan", "Allen")) |>
  rename(Sex = Gender) |>
  group_by(Year, Name) |>
  summarize(Count = sum(Count)) |>
  ggplot(mapping = aes(x = Year, y = Count, color = fct_reorder(Name, Count, .desc = TRUE))) +
  geom_line() +
  labs(y = NULL, title = "Number of babies named Alan, Allan, or Allen over the years",
       color = "Name")
```

```{r q9}
names_a |>
  filter(Name %in% c("Alan", "Allan", "Allen"),
         Year == 2000, State %in% c("PA", "CA")) |>
  rename(Sex = Gender) |>
  group_by(Name, State) |>
  summarize(Count = sum(Count), .groups = "drop") |>
  pivot_wider(names_from = Name, values_from = Count, values_fill = 0) |>
  knitr::kable(format = "html", 
               caption = "Number of babies named Alan, Allan, or Allen by state") |>
  kableExtra::kable_styling(bootstrap_options = "striped", 
                            font_size = 14)
```

```{r q10}
names_a |>
  filter(Name %in% c("Alan", "Allan", "Allen"),
         Year == 2000, State %in% c("PA", "CA")) |>
  rename(Sex = Gender) |>
  group_by(Name, State) |>
  summarize(Count = sum(Count), .groups = "drop") |>
  group_by(State) |>
  mutate(Count = Count / sum(Count)) |>
  pivot_wider(names_from = Name, values_from = Count, values_fill = 0) |>
  gt() |>
  tab_header(title = "Proportion of babies named Alan, Allan, or Allen by state") |>
  fmt_percent(columns = 2:4, decimals = 2)
```
